\subsection{Outreach Program}

Our outreach program has two primary objectives. The first is to promote the interrelated STEM disciplines, Science, Technology, Engineering, and Mathematics, and highlight their distinct but interconnected nature. These four fields are essential in shaping the future of technological advancements and scientific discoveries, and we aim to inspire the next generation to pursue careers in STEM-related fields.

The second objective of our outreach program is to popularize the space sector and space exploration. We aim to educate the public about the importance of space technologies and how they impact our daily lives. 
%Furthermore, we want to showcase the role of CanSats in space exploration and highlight the various stages involved in their development, from design to launch. 
Through our outreach efforts, we hope to inspire the public to take an interest in space exploration and encourage the pursuit of careers in the space industry.

The team has made a detailed plan for raising awareness of the CanSat project and getting people involved. Different actions are included in this outreach plan to get the word out about the project. These include:
\begin{multicols}{2}[\vspace{-0.5\baselineskip}]
        \begin{itemize}[leftmargin=1cm,itemindent=0.5cm,noitemsep, topsep=0pt, label=$\bullet$]
%\begin{itemize}[, noitemsep, topsep=0pt]
\item presentations
% \item workshops
\item demonstrations
\item social media
\item websites
\item community engagement
\item participation in science fairs or events.
\end{itemize}
\end{multicols}
\vspace*{-0.5\baselineskip}

In our outreach plan, we aim to target specific audiences, deliver clear messages, and use various media to achieve our goals. We will present the CanSat project to different groups such as schools and community centers, focusing on the technology it uses and its applications. These presentations aim to increase awareness and inspire interest in STEM fields among students and the community.

We will use social media platforms like Twitter, Instagram, and Facebook to document our team's progress and share updates about the project with the public. Additionally, a dedicated website will be developed to provide detailed information, including progress updates, photos, videos, and data from the mission. This approach ensures regular communication about our challenges and successes, fostering engagement and creating a sense of community around the project.

For science fairs and events, we will target students, teachers, and the public interested in STEM education and space technology. Our message will highlight how the CanSat project can drive innovation and solve real-world problems, encouraging participants to explore STEM careers. By focusing on these activities, we aim to increase interest and involvement in the CanSat project and promote the importance of space technology and STEM education.

 



% \begin{table}[ht]
% \centering
% \begin{tabular}{|>{\centering\arraybackslash}p{2.2cm}|p{3cm}|p{3cm}|p{3cm}|p{3cm}|}
% \hline
% Activities & Audience & Message & Medium & Outcome\\
% \hline
% Presentations and workshops & Schools, community groups, and other organizations interested in STEM education & 
% Importance of STEM fields, the relevance of CanSat technology, and the process of designing and building a CanSat& 
% PowerPoint presentations and interactive demonstrations using physical models or simulators & 
% Increase awareness and interest in the CanSat project and inspire the audience to pursue STEM-related fields\\
% Social media and websites & General public, including students, teachers, parents, and space enthusiasts & Providing regular updates about the CanSat project, including its progress, challenges, and successes &  Text, photos, and videos & Increase engagement and interest in the CanSat project and to create a sense of community around it\\
% Community engagement activities & Local communities, including students, teachers, parents, and members of the public & Importance of STEM fields and the potential of CanSat technology to inspire innovation and problem-solving & 
% Interactive discussions, Q\&A sessions, and hands-on demonstrations of CanSat models or simulators & 
% Foster a sense of community engagement and to increase interest and awareness of the CanSat project and STEM fields\\
% Science fairs or events & Students, teachers, and members of the public interested in STEM education and space technology &Showcasing the CanSat project and its potential to inspire innovation and problem-solving & Physical demonstrations of CanSat models or simulators and interactive discussions about the CanSat project & Increase awareness and interest in the CanSat project and to inspire the next generation of space enthusiasts and innovators\\
% \hline
% \end{tabular}
% \caption{Outreach activities.}
% \end{table}